Manuscript Template for a Data Analysis Project

### 2023-02-03 products/manuscript/MANU.qmd
commit

---
title: "Manuscript Template for a Data Analysis Project"
subtitle: "Exploring Factors influencing HIV Death-to-Case ratio in the United States and Puerto Rico -- 2020"
author: Hayley Hemme
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../dataanalysis_template_references.bib
csl: ../apa.csl
---

>>>>

---
title: "Manuscript Template for a Data Analysis Project"
subtitle: "Exploring Factors influencing HIV-related Mortality Rates in the Georgia -- 2018 - 2020"
author: Hayley Hemme
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../dataanalysis_template_references.bib
csl: ../apa.csl
---
